An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-06-28 gas-adsorption/referee-response.md

Referee 1 states that "Phenomenological predictions without any relation to real
materials are not very helpful, if not useless."  The referee fails to grasp
that our theory *does* take into account the gas, and places a fundamental limit
on the capacity of an entire class of materials (inflexible porous materials).
This is far from useless.  The referee suggests as superior an approach
involving screening hundreds of thousands of actual MOFs.  We will point out
that such an approach cannot possibly determine that there isn't a better MOF
out there, while our approach can do so.

TODO: We should find a place to edit the paper to make this more clear, and
state here that we did so.

The referee gives a litany of structural properties that we do not address in
our model: "pore volume, pore size, specific surface area, crystal density,
skeletal density, packing density, different adsorption sites etc."

    We note that some of these (e.g. crystal density, skeletal density)
    manifestly have no impact on the property we are studying, which is
    volumetric storage capacity.  Others of course do impact the volumetric
    storage capacity of a material, but do not relate to an upper bound
    specifically.

    As discussed in the second and third paragraphs of the results section, our results do put a lower bound of 85% on the void fraction for any porous material that will meet the ARPA-E target for methane volumetric deliverable capacity, and a lower bound of 94% for a material reaching the DOE ULTIMATE target for hydrogen at 298K.  These results *can* guide exploration, if we assume that reaching those targets is the goal.

### 2021-07-06 gas-adsorption/referee-response.md

1. The referee suggests that we attempt to quantify the possible effect of a
   flexible MOF on our upper bound.

We have added a section "Flexible two-phase model" discussing flexible MOFs. We
cannot place a formal upper bound on a flexible MOF in general, but we can put
an upper bound on the capacity of a two-phase MOF such as Co(bdp), if we
constrain the free energy difference between the two phases. This suggests that
this type of a system will require a more stable closed phase in order to reach
the DOE targets.

1. The referee asks that we provide some guidelines in terms of working
   conditions to reach the DOE target.  They further suggest looking at a
   temperature difference to see how that could impact the deliverable capacity.

We added a sentence mentioning that we cannot apply our upper bound in the case
where the temperature is changed, because a uniform potential may no longer lead
to the optimal deliverable capacity.

### 2021-07-06 gas-adsorption/rsc-gas-ads-complete.tex
added note about temperature-pressure swings, and a davidsays that I wonder if we *can* do something here

The first limitation of our proof is that we restricted ourselves to
\emph{isothermal} pressure swing storage (which is consistent with the targets set by DOE). By raising the temperature of the
adsorbent during gas discharge to drive off residual
gas~\cite{gomez2014exploring}, the deliverable capacity could be enhanced,
albeit at the cost of a more complicated engineering design of the fuel tank
and vehicle.

>>>>

\startreferees{Added last sentence to clarify why we cannot place a bound
  on the deliverable capacity when the temperature is changed.}

The first limitation of our proof is that we restricted ourselves to
\emph{isothermal} pressure swing storage (which is consistent with the targets set by DOE). By raising the temperature of the
adsorbent during gas discharge to drive off residual
gas~\cite{gomez2014exploring}, the deliverable capacity could be enhanced,
albeit at the cost of a more complicated engineering design of the fuel tank
and vehicle.
%
We cannot place an upper bound on such a process using our approach because with
changing temperature a uniform potential may not give the maximum deliverable
capacity.  \davidsays{As far as I can intuit, \emph{normally} the entropy
increases with temperature, and if that is the case then a uniform potential
will give the optimum deliverable capacity.  If we can prove that for a subset
of substrate interactions (e.g. when the substrate acts as an external potential
felt by the gas), the optimal potential is uniform then we could apply our model
to temperature-pressure swings.}
